Online appendix for "Derogations, Democratic Backsliding, and International Human Rights During the COVID-19 Pandemic

### 2024-07-17 manuscript/appendix.qmd
Remove old crossref stuff

---
title: 'Online appendix for "Derogations, Democratic Backsliding, and International Human Rights During the COVID-19 Pandemic"'
short-title: 'Online appendix for "Derogations and Backsliding"'
author:
- name: Suparna Chaudhry
  affiliation: Lewis and Clark College
  orcid: 0000-0003-3506-7590
  url: https://www.suparnachaudhry.com/
  email: schaudhry@lclark.edu
- name: Audrey L. Comstock
  affiliation: Arizona State University
  orcid: 0000-0003-1772-5350
  url: https://audreylcomstock.weebly.com/
  email: audrey.comstock@asu.edu
- name: Andrew Heiss
  affiliation: Georgia State University
  orcid: 0000-0002-3948-3914
  url: https://www.andrewheiss.com
  email: aheiss@gsu.edu
date: 2024-06-30
code-repo: "Access the code, data, and analysis at <https://github.com/andrewheiss/lemon-lucifer>"
bibliography: references.json
csl: csl/apa.csl
link-citations: true
# crossref:
#   tbl-title: "Table&nbsp;A"
#   tbl-prefix: "Table&nbsp;A"
#   fig-title: "Figure&nbsp;A"
#   fig-prefix: "Figure&nbsp;A"
crossref:
  custom:
    - kind: float
      key: appfig
      latex-env: appfig
      reference-prefix: Figure A
      space-before-numbering: false
      latex-list-of-description: Appendix Figure
    - kind: float
      key: apptbl
      latex-env: apptbl
      reference-prefix: Table A
      space-before-numbering: false
      latex-list-of-description: Appendix Table
apptbl-cap-location: top
toc: true
toc-depth: 2
---

>>>>

---
title: 'Online appendix for "Derogations, Democratic Backsliding, and International Human Rights During the COVID-19 Pandemic"'
short-title: 'Online appendix for "Derogations and Backsliding"'
author:
- name: Suparna Chaudhry
  affiliation: Lewis and Clark College
  orcid: 0000-0003-3506-7590
  url: https://www.suparnachaudhry.com/
  email: schaudhry@lclark.edu
- name: Audrey L. Comstock
  affiliation: Arizona State University
  orcid: 0000-0003-1772-5350
  url: https://audreylcomstock.weebly.com/
  email: audrey.comstock@asu.edu
- name: Andrew Heiss
  affiliation: Georgia State University
  orcid: 0000-0002-3948-3914
  url: https://www.andrewheiss.com
  email: aheiss@gsu.edu
date: 2024-06-30
code-repo: "Access the code, data, and analysis at <https://github.com/andrewheiss/lemon-lucifer>"
bibliography: references.json
csl: csl/apa.csl
link-citations: true
crossref:
  custom:
    - kind: float
      key: appfig
      latex-env: appfig
      reference-prefix: Figure A
      space-before-numbering: false
      latex-list-of-description: Appendix Figure
    - kind: float
      key: apptbl
      latex-env: apptbl
      reference-prefix: Table A
      space-before-numbering: false
      latex-list-of-description: Appendix Table
apptbl-cap-location: top
toc: true
toc-depth: 2
---
